---
title: "Activity 6 - Logistic Regression"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Libraries
```{r libraries, message=FALSE}
library(tidyverse)
library(tidymodels)
```

## The Data
```{r Data, message=FALSE}
resume <- readr::read_csv("https://www.openintro.org/data/csv/resume.csv")
```
The variable of interest is `received_callback`, which is a binary variable.

```{r target visualization}
resume %>% 
  ggplot(aes(x=received_callback==1)) + 
  geom_bar() + 
  theme_bw() + 
  ylab("Count") + 
  xlab("Received Call Back") + 
  ggtitle("# of Received call Back")
```

```{r summary table}
# TODO Add Percentages
resume %>% 
  group_by(received_callback) %>% 
  summarise(n()) %>% 
  knitr::kable()
```
The probability of someone getting a call back from their resume is 8.05% or 392/(4478+392). The odds of someone getting a call back is 8.75% or 392/4478.

## Logistic Regression
```{r summary black/white}
resume %>% 
  group_by(received_callback, race) %>% 
  summarise(n()) %>% 
  knitr::kable()
```
The probability that a randomly selected résumé/person perceived as Black will be called back is 6.45%.
The odds that a randomly selected résumé/person perceived as Black will be called back is 6.89%.

### Logistic Model
```{r logistic model}
# The {tidymodels} method for logistic regression requires that the response be a factor variable
resume <- resume %>% 
  mutate(received_callback = as.factor(received_callback))

resume_mod <- logistic_reg() %>%
  set_engine("glm") %>%
  fit(received_callback ~ race, data = resume, family = "binomial")

tidy(resume_mod) %>% 
  knitr::kable(digits = 3)
```
The regression equation corresponding to résumés/persons perceived as White is `received_callback = 0.438(racewhite) - 2.675`. 

The *simplified* estimated regression equation corresponding to résumés/persons perceived as Black is `received_callback = ???? (raceblack) + 2.675``
